\begin{thebibliography}{10}

\bibitem{ref:Baader00}
F. Baader, D. Calvanese and D. L. McGuinness, D. Nardi, P. F. Patel-Scheider (Edt), The Description Logic Handbook: Theory, Implementation, and Applications, $2^{nd}$ edition, 2007.

\bibitem{ref:Baader01}
F. Baader and U. Sattler, An Overview of Tableau Algorithms for Description Logics, Studia Logica, Volume 69, Pages: 5--40, Springer, 2001.

\bibitem{ref:Baader02}
F. Baader, J. Hladik, C. Lutz and F. Wolter, From Tableaux to Automata for Description Logics, Fundamenta Informaticae, Volumn 57, Pages: 1--33, 2003.

\bibitem{ref:Brachman}
R. J. Brachman and J. G. Schmolze, An Overview of  the  \textsc{KL-one} Knowledge  Representation System, Cognitive Science, Vol 9, Pages: 171--216, 1985.

\bibitem{ref:Calvan}
D. Calvanese, M. Lenzerini and D. Nardi, Description Logics for Conceptual Data Modeling, Logics for Databases and Information Systems, Kluwer Academic Publisher, 1998.

\bibitem{ref:Horrock00}
I. Horrocks and U. Sattler, A Description Logic with Transitive and Inverse Roles and Role Hierarchies, Journal of Logic and Computation, Volumn 9(3), Pages: 385--410, 1999.

\bibitem{ref:Horrock01}
I. Horrocks, U. Sattler and S. Tobies, A $\textsc{PSPace}$-Algorithm for Deciding $\mathcal{ALCNI}_{\mathcal{R}^+}$-Satisfiability, LTCS-Report 98-08, 2000.

\bibitem{ref:Sahoo}
S. S. Sahoo and K. Thirunarayan, Tableau Algorithm for Concept Satisfiability in Description Logic $\mathcal{ALCH}$, TR-2009-07, 2009.

\bibitem{ref:Schimidt}
M. Schmidt-Schau\ss and G. Smolka, Attributive Concept Descriptions with Complements, Artificial Intelligence, Volumn 48, Pages: 1--26, Elsevier, 1991.

\bibitem{ref:Tobies}
S. Tobies, Complexity Results and Practical Algorithms for Logics in Knowledge Representation, Diploma Thesis, 2001.

\end{thebibliography}